Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

Our approach largely builds on \cite{adv_upd}, who identified the
collapse of Q-learning for small time steps and suggested advantage
updating with proper $\deltat$ scalings as a solution.

>>>>

Our approach builds on \cite{adv_upd}, who identified the
collapse of Q-learning for small time steps and suggested the Advantage
Updating algorithm with proper $\deltat$ scalings as a solution; testing
was only done on a quadratic-linear problem. Our Deep Advantage Updating
reuses this idea with a different normalization step for $A$ (which
forgoes the need to learn the normalization itself, thanks to the
parameterization \eqref{eq:Aparam}), and tests Advantage Updating for the
first time on a variety on RL environments using deep networks.
Additionally, we provide formal proofs for the collapse
of Q-learning when $\deltat\to 0$, and the non-collapse of Advantage
Updating.

\TODO{Say that Actor-critic has no problem when $\deltat\to 0$?}
